First, we will have a dataset with 29 states of America. Each state hs completed data for the population of home school enrollment from 2017- 2022.(6 years)

```{r}
library(dplyr)
library(ggthemes)
library(magick)
# read the data
school_state <- read.csv("../data/derived/state_update.csv")
print(summary(school_state))
# group by state and count
grouped_school_state <- school_state %>% group_by(state) %>% 
  summarise(count = n())
```

Here is a raw graph showing all the states provided from the dataset and the population change over 6 years.
```{r}
library(ggplot2)
ggplot(school_state, aes(x = year, y = homeschool_students, group = state, color = state)) +
  geom_line() +
  geom_point() + 
  theme_minimal() +
  labs(title = "Population Change Over 6 Years for 29 States",
       x = "Year",
       y = "Population") +
    theme(legend.position = "right",  # Positions the legend on the right
        legend.title = element_text(face = "bold"),  # Bold legend title
        legend.text = element_text(size = 6),  
        legend.key.size = unit(0.5, "cm"), 
        legend.box.background = element_rect(colour = "black", linewidth = 0.2), 
        legend.spacing.x = unit(0.1, "cm"), 
        legend.box = "vertical")  
```

Based on the graph, we can find out there are several states with obvious trends, which is "FLORIDA", "GEORGIA", "CALIFORNIA" and "VIRGINIA"
To find out which states have fluctuated the growth the most from 2017-2023, I first explore and calculate all the growth rate for each year's states.

```{r}
source('../analyses/helper-function/growth_rate.R')
growth_df <- calculate_growth_proportion(school_state, "state", "year", "homeschool_students")
growth_df
```
Then I first sort the calculated growth rate by the absolute growth rate in descending order and select top 3 states' name.
Also, according to the same calculated dataframe, I group it by years and try to select the top 5 most fluctuated states each year. Counting the appearance of states in top 5 and still choose the first three. 
At last, I intersect two dataframes to get the most important state over years' home school growth rate.
```{r}
#df1
top_three_df1 <- growth_df  %>% 
  ungroup   %>% 
  arrange(desc(abs_growth)) %>%  # Sort the data frame in descending order by the 'abs_growth' column
  slice_head(n = 3)  # Get the top 3 state
#df2
top_three_df2 <- growth_df %>%
  arrange(desc(abs_growth)) %>%  # Sort in descending order of proportion
  group_by(year) %>%  # Group by year
 # arrange(desc(year)) %>%  # Within each group, sort in descending order of year
  top_n(5) %>%  # Select top ten rows for each year
  group_by(state) %>%  # Group by State
  summarise(count = n()) %>% # Count the number of occurrences of each state
  arrange(desc(count)) %>%
  slice_head(n = 3)

intersection <- intersect(top_three_df1$state, top_three_df2$state)

```

```{r}
selected_states <- c(intersection,"FLORIDA", "GEORGIA", "CALIFORNIA", "VIRGINIA","KENTUCKY")
# Filter growth_df for the selected states, get distinct abbreviations along with their corresponding state
selected_states_abbre <- school_state %>%
  ungroup() %>%  
  filter(state %in% selected_states) %>%
  select(state, Abbreviation) %>%  # Select both state and Abbreviation to keep the grouping context
  distinct()

```


```{r, warning=FALSE}
special_theme = theme(
  # set the plot ratio
  aspect.ratio = 2/5,
  # set the title size and adjust its position
  plot.title = element_text(size = unit(11, "pt"),hjust = 0,vjust = -5),
  # set the subtitle size and adjust its position
  plot.subtitle = element_text(size = unit(9.5, "pt"),hjust = 0,vjust = -7),
  # set the legend size and adjust its position
  legend.title = element_text(size = unit(7.5, "pt")),
  legend.key.size = unit(7.5, "pt"),
  legend.margin = margin(t = 20, r = 0, b = 0, l = -228, unit = "pt"),
  legend.text = element_text(size = unit(7.5, "pt")),
  # set the caption size and color 
  plot.caption = element_text(hjust = 0, vjust = 2, size = unit(6.5, "pt"), colour = "#404040"),
  # the economist style does not include x and y title, so I hide them
  axis.title.x =  element_blank(),
  axis.text.x = element_text(angle = 0, vjust = 6, hjust = 0.5,size = unit(7, "pt")),
  axis.text.y.right  = element_text(size = unit(7, "pt"),hjust = 1, vjust = -0.5),
  # Hide the default y-axis title
  axis.title.y = element_blank(),  
  # the major grid line should be grey with specific thickness
  panel.grid.major = element_line(color = "#B7C6CF", linewidth = unit(0.5, "pt")),
  # the x line should be black with specific thickness
  axis.line.x  = element_line(color = "black", linewidth = unit(0.4, "pt")),
  plot.margin = margin(t = 0, r = -10, b = 0, l = 0, unit = "pt"),
  # set the background to be white for new web version
  panel.background = element_rect(fill = "white", colour = NA),
  plot.background = element_rect(fill = "white", colour = NA)
  )

#new data frame with only those 6 focus areas
highlight_data <- school_state %>%
  filter(Abbreviation %in% selected_states_abbre$Abbreviation)

highlight_colors <- c("#17648d", "#51bec7", "#d6ab63",  "#843844", "#008c8f","#a885ac")
years_to_include <- unique(c(school_state$year))
#selection of 5 focus areas
names(highlight_colors) <- selected_states_abbre$Abbreviation
# line plot
plots = ggplot(school_state, aes(x = year, y = homeschool_students, group = Abbreviation))+
  theme_economist() + #using the economist theme
  geom_line(linewidth = 0.25, color = '#d4dddd') + geom_line(data = highlight_data, aes(color = Abbreviation), linewidth = 0.6) +
  scale_colour_manual(values = highlight_colors) + 
  scale_y_continuous(position = "right",labels = scales::label_number_si())+
  scale_x_discrete(limits = years_to_include, expand = c(0, 0.3))+
  labs(title = "American Home schooling ",
       subtitle = "Enrollments from 2017 - 2023",
       caption = "Source: Data from The Post's analysis of home-schooling enrollment across the US",
       y = "Population", x = "Year", color = "State") +
  special_theme
# first save the graph
ggsave("../output/state.png",plots,width = 5, height =3,dpi = 300, units = "in")
# add up the red square as it should be a plot for economist using the libarary magick
plot_state <- image_read("../output/state.png")
head <- image_read("../data/Figure/header2.png")
#update my plot
plot_update <- image_flatten(c(plot_state,head))
image_write(plot_update, "../output/state_update.png")
```

