**To deal with the NAs in our datasets**
```{r}
library(dplyr)
# read the data
school_state <- read.csv("../../data/raw/home_school_state.csv")
print(summary(school_state))
# group by state and count
grouped_school_state <- school_state %>% group_by(state) %>% 
  summarise(count = n())
grouped_school_state
```
By discovering the dataset, there are 33 states, each with 2017-2022 population of home-school enrollment. However, the data has missing NA. I first delete all the states with incomplete data.
```{r}
# deal with nas
rows_with_na <- apply(school_state, 1, function(row) any(is.na(row)))
# lists of state names which have NAs
missing_state <- unique(school_state[rows_with_na, "state"])
# filter and get a new dataset
homeschool_update <- school_state %>% filter(!state %in% missing_state)
#check if there is still nas
summary(homeschool_update) 
# group by state and count
group_state = homeschool_update %>% group_by(state) %>% 
  summarise(count = n())
group_state
```
Thus, we will have a dataset with 29 states of America. Each state hs completed data for the population of home school enrollment from 2017- 2022.(6 years)

```{r}
head(homeschool_update)
```
Save the data to derived folder for further use.
```{r}
write.csv(homeschool_update, "../../data/derived/state_update.csv",row.names = FALSE) 
```


# Delete NAs and 0 and change year for district dataset

```{r}
school_district <- read.csv("../../data/raw/home_school_district.csv")
school_district
school_district$year <- sub("^(....)-.*", "\\1", school_district$year)
school_district
```

```{r}
# group by state and count
grouped_school_district <- school_district %>% group_by(lea_name) %>% 
  summarise(count = n())
grouped_school_district
# deal with nas
rows_with_na <- apply(school_district, 1, function(row) any(is.na(row)))
# lists of state names which have NAs
missing_names <- unique(school_state[rows_with_na, "lea_name"])
# Filter out rows from school_district where lea_name is NA or lea_name is in the list of missing_names,
# and also remove rows where 'homeschool_students' is 0
homeschool_district_update <- school_district %>%
  filter(!is.na(lea_name) & !(lea_name %in% missing_names) & homeschool_students != 0)

#check if there is still nas
summary(homeschool_district_update) 
# group by state and count
grouped_school_district= homeschool_district_update %>% group_by(lea_name) %>% 
  summarise(count = n())%>%
  filter(count == 6) %>% select(lea_name)
filtered_school_district <- school_district %>%
  filter(lea_name %in% grouped_school_district$lea_name)
filtered_school_district
```
```{r}
write.csv(filtered_school_district, "../../data/derived/district_update.csv",row.names = FALSE) 
```





